---
title: "Data Analysis (Prof. Ugo Ala) - R Practical N"
author: "Cognome Nome, Cognome Nome, Cognome Nome"
date: "01-01-0000"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
    toc: true
    toc_depth: 2
header-includes:
  - \usepackage{fvextra}
  - \usepackage{fancyhdr}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere=true,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \renewcommand{\contentsname}{Index}
  - \AtBeginDocument{
      \pagestyle{fancy}
      \fancyhead[L]{}
      \fancyhead[R]{}
      \fancyhead[C]{Data Analysis - R Practical N - 01-01-0000 - Cognome N., Cognome N., Cognome N.}
      \fancyfoot[C]{\thepage}
      \renewcommand{\sectionmark}[1]{}
      \renewcommand{\subsectionmark}[1]{}
    }
---

\thispagestyle{empty}

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

# Introduction

## Environment

The exrcise was run in a Docker, the image can be pulled from GitHub:

```sh
docker pull ghcr.io/maiolino-au/data_analysis:latest
```

You can run it with (regardless of the version):

* In Windows

```powershell
@echo off
set "CURRENT_DIR=%cd%"
docker run -it --rm -p 8787:8787 -v "%CURRENT_DIR%:/sharedFolder" ghcr.io/maiolino-au/data_analysis:latest
```

* In Linux / MacOS

```sh
docker run -it --rm -p 8787:8787 -v .:/sharedFolder ghcr.io/maiolino-au/data_analysis:latest
```

Repository link: https://github.com/Maiolino-Au/Data_Analysis

The datas used are availabe at:

The scripts assume that the working directory is the same where the data are stored.

\newpage

## Working directory and Packages

First of all, we need to set the correct working directory: all the commands assume that the datas are stored in the working directory. I worked in a docker container to which i have shared a directory from my PC, called `/sharedFolder` inside the docker. In the directory there is one specific for this lesson, called `Practical_1`. Therefore:

```{r, eval=T, echo=T}
setwd("/sharedFolder/Practical_1/")
```

Then we need to load the packages we are going to use. I used `suppressPackageStartupMessages()` to avoid printing all the startup messages of each package.

```{r, eval=T, echo=T}
suppressPackageStartupMessages({
    library(phyloseq)
    library(dplyr)
    library(tidyr)
    library(stringr)
    library(microbiome)
    library(microbial)
    library(vegan)
    library(usedist)
    library(ggplot2)
    library(nortest)
    library(car)
})
```

\newpage

## Notes

